### 2017-05-13 paper/evaluation.tex
fix

\sloppy Figures~\ref{fig:longtcost} and~\ref{fig:medtcost} show the
time distribution of individual test cases per project.  We observed
that the average median value of execution cost for a test was
relatively small (dashed horizontal red lines), namely 0.31s for
\medg{} projects and 0.23s for \longg{} projects.  The standard
deviations associated with each distribution were relatively
low.\Comment{ Figure~\ref{fig:sd} shows the number of projects within
  specific ranges of $\sigma$ values.}  We noted a small number of
cases of CPU monopolization.  For example, the highest value of
$\sigma$ occurred in \CodeIn{uber\_chaperone}, a project from the
medium group.  This project contains only 65 tests, 62 of which take
less than 0.5s to run, one of which takes nearly 3s to run, and two of
which take $\sim$40m to run.  For this project, 99.2\% of the
execution cost is dominated by only 3\% of the tests; without these
two costly tests this project would have been classified as
short-running.  A closer inspection in the data indicates that the
project \CodeIn{uber\_chaperone} was a corner case; we did not find
other projects with such extreme time monopolization profile.  Project
\CodeIn{facebookarchive\_linkbench} is also classified as long-running
and has the second highest value of $\sigma$.  For this project,
however, cost is distributed more smoothly across \Fix{98} tests, of
which \Fix{8 (8.1\%)} take more than \Fix{1s} to run with the rest of
the tests running faster.

@@

\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
  \footnotesize
  %  \small
  \centering
  \setlength{\tabcolsep}{2.5pt}
%    \resizebox{.48\textwidth}{!}{%
    \begin{tabular}{lrr}
        \toprule
        \emph{Subject} & \emph{\# of modules} & \emph{Mode}\\%
        \midrule%
        \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1/1 &  \ParClassSeqMeth{}\\%
        \Comment{Apache }Flink & 74/74 & \ForkSeq{} \\%        
        \Comment{JenkinsCI }Gerrit\Comment{ Trigger Plugin} & 1/1 & \ForkSeq{}\\%
        \Comment{Spotify }Helios & 8/8 & \ForkSeq{}\\%
        Javaslang & 3/3 & \ParClassParMeth{}\\%
        Jcabi\Comment{ Github} & 1/1 & \ParClassParMeth{}\\%        
        \Comment{Hazelcast }Jet & 7/14 & \ForkSeq{}\\%
        \Comment{Apache Logging }Log4J2 & 25/31 & \ForkSeq{}\\%
        \Comment{Jankotek }MapDB & 1/2 & \ParClassParMeth{}\\%        
        \bottomrule%
    \end{tabular}
    \caption{Subjects with parallel test execution enabled by
    default.}
    \label{tab:freqmodes-dynamic}
\end{wrapfigure}
Figure~\ref{tab:freqmodes-dynamic} shows the projects we idendified
where parallelism is enabled by default in Maven.  Column
``\emph{Subject}'' indicates the name of the project, column
``\emph{\# of modules}'' indicates the fraction of modules containing
tests that use the configuration of parallelism mentioned in column
``\emph{Mode}''.  We note that, considering these projects, the
modules that do not use the configuration cited use the sequential
configuration \Seq{}.  For example, six modules (=31-25) from Log4J2
use sequential configuration.

>>>>

\sloppy Figures~\ref{fig:longtcost} and~\ref{fig:medtcost} show the
time distribution of individual test cases per project.  We observed
that the average median value of execution cost for a test was
relatively small (dashed horizontal red lines), namely 0.31s for
\medg{} projects and 0.23s for \longg{} projects.  The standard
deviations associated with each distribution were relatively
low.\Comment{ Figure~\ref{fig:sd} shows the number of projects within
  specific ranges of $\sigma$ values.}  We noted a small number of
cases of CPU monopolization.  For example, the highest value of
$\sigma$ occurred in \CodeIn{uber\_chaperone}, a project from the
medium group.  This project contains only 65 tests, 62 of which take
less than 0.5s to run, one of which takes nearly 3s to run, and two of
which take $\sim$40m to run.  For this project, 99.2\% of the
execution cost is dominated by only 3\% of the tests; without these
two costly tests this project would have been classified as
short-running.  A closer inspection in the data indicates that the
project \CodeIn{uber\_chaperone} was a corner case; we did not find
other projects with such extreme time monopolization profile.  Project
\CodeIn{facebookarchive\_linkbench} is also classified as long-running
and has the second highest value of $\sigma$.  For this project,
however, cost is distributed more smoothly across 98 tests, of
which 8 (8.1\%) take more than 1s to run with the rest of
the tests running faster.

@@

\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
  \footnotesize
  %  \small
  \centering
  \setlength{\tabcolsep}{2.5pt}
%    \resizebox{.48\textwidth}{!}{%
    \begin{tabular}{lrr}
        \toprule
        \emph{Subject} & \emph{\# of modules} & \emph{Mode}\\%
        \midrule%
        \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1/1 &  \ParClassSeqMeth{}\\%
        \Comment{Apache }Flink & 74/74 & \ForkSeq{} \\%        
        \Comment{JenkinsCI }Gerrit\Comment{ Trigger Plugin} & 1/1 & \ForkSeq{}\\%
        \Comment{Spotify }Helios & 8/8 & \ForkSeq{}\\%
        Javaslang & 3/3 & \ParClassParMeth{}\\%
        Jcabi\Comment{ Github} & 1/1 & \ParClassParMeth{}\\%        
        \Comment{Hazelcast }Jet & 7/14 & \ForkSeq{}\\%
        \Comment{Apache Logging }Log4J2 & 25/31 & \ForkSeq{}\\%
        \Comment{Jankotek }MapDB & 1/1 & \ParClassParMeth{}\\%        
        \bottomrule%
    \end{tabular}
    \caption{Subjects with parallel test execution enabled by
    default.}
    \label{tab:freqmodes-dynamic}
\end{wrapfigure}
Figure~\ref{tab:freqmodes-dynamic} shows the projects we idendified
where parallelism is enabled by default in Maven.  Column
``\emph{Subject}'' indicates the name of the project, column
``\emph{\# of modules}'' indicates the fraction of modules containing
tests that use the configuration of parallelism mentioned in column
``\emph{Mode}''.  We note that, considering these projects, the
modules that do not use the configuration cited use the sequential
configuration \Seq{}.  For example, six modules (=31-25) from Log4J2
use sequential configuration.
